Fourmile_inputs

### 2022-09-27 fourmile_inputs.Rmd
still working on precip, everything else is ready

#daily precip
precall <- prec %>%
  mutate(date = dmy(date),
         doy = yday(date)) %>%
  mutate_at(c('Gordon_South', 'Gordon_North',
              'GH', 'LM', 'SE', 'SP', 'ST', 'NADP_SL'),
            ~(ifelse(!doy %in% c(152:258),

  mutate_at(c('prism_W', 'prism_M', 'prism_E'), ~(ifelse(doy %in% c(152:258),
                                                         NA, .))) %>%
  filter(date > '2009-12-31') %>%
  dplyr::select(-c(doy)) %>%
  mutate(date = format(as.Date(date), '%d.%m.%Y'))

  mutate(prism_most_mm = prism_mm * 0.974,
         prism_little_mm = prism_mm * 0.026) %>%
  mutate_at(c('prism_most_mm'), list(lead), n = 1) %>%
  mutate(prism_new_mm = prism_most_mm + prism_little_mm

>>>>

#daily precip
precall <- prec %>%
  mutate(date = dmy(date),
         doy = yday(date)) %>%
  mutate_at(c('Gordon_South', 'Gordon_North',
              'GH', 'LM', 'SE', 'SP', 'ST', 'NADP_SL'),
            ~(ifelse(!doy %in% c(152:258),
                               NA, .))) %>%
  mutate(prism_most_w = prism_W * 0.974,
         prism_little_w = prism_W * 0.026,
         prism_most_m = prism_M * 0.974,
         prism_little_m = prism_M * 0.026,
         prism_most_e = prism_E * 0.974,
         prism_little_e = prism_E * 0.026) %>%
  mutate_at(c('prism_most_w', 'prism_most_m', 'prism_most_e'), list(lead), n = 1) %>%
  mutate(prism_W = prism_most_w + prism_little_w,
         prism_M = prism_most_m + prism_little_m,
         prism_E = prism_most_e + prism_little_e) %>%
  dplyr::select(-c(prism_most_w, prism_little_w,
                   prism_most_m, prism_little_m,
                   prism_most_e, prism_little_e)) %>%
  mutate_at(c('prism_W', 'prism_M', 'prism_E'), ~(ifelse(doy %in% c(152:258),
                                                         NA, .))) %>%
  filter(date > '2009-12-31')

bet_rain <- bet_met %>%
  dplyr::select(c(5,6)) %>%
  rename(Betasso_rain =1) %>%
  mutate(date = as.Date(DATE_TIME)) %>%
  group_by(date) %>%
  summarize(Betasso = sum(Betasso_rain)) %>%
  filter(date > '2009-12-31')

precall <- full_join(precall, bet_rain, by = 'date')

updated_prec <- updated_prec %>%
  mutate_at(c(2,4,6,8,10), ~(.*25.4)) %>%
  rename(GH = 2,
         LM = 4,
         SE = 6,
         SP = 8,
         ST = 10)

gh <- updated_prec %>%
  dplyr::select(c(1,2)) %>%
  mutate(date = mdy(GH_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE)

lm <- updated_prec %>%
  dplyr::select(c(3,4)) %>%
  mutate(date = mdy(LM_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE)

se <- updated_prec %>%
  dplyr::select(c(5,6)) %>%
  mutate(date = mdy(SE_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE)

sp <- updated_prec %>%
  dplyr::select(c(7,8)) %>%
  mutate(date = mdy(SP_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE)

st <- updated_prec %>%
  dplyr::select(c(9,10)) %>%
  mutate(date = mdy(ST_date)) %>%
  dplyr::select(-c(1)) %>%
  distinct(date, .keep_all = TRUE)

write.csv(gh, 'gh.csv')
write.csv(lm, 'lm.csv')
write.csv(se, 'se.csv')
write.csv(sp, 'sp.csv')
write.csv(st, 'st.csv')

write.csv(precall, 'precall_fix.csv')

# mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
#   replace(is.na(.), -9999) %>%
#   dplyr::select(-c(doy))
